### 2016-11-16 ms/ms.tex
added main file that runs all analysis, fixed bug where the sum instead of the mean was taken to create networks

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[the "rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that phenologically new plant and pollinator species tended to
interact with already well-connected species, potentially because
these species are either more abundant or more temporally
persistent. In addition, using a space-for-time substitution to study
primary succession along a glacier foreland, \cite{albrecht2010plant}
also found some evidence that assembly occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}.  An
increase in nestedness could result from the preferential attachment
process where specialist species attach to the well-connected,
generalist core.

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially "applied succession"
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. To ensure the continued provision
of ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, kremen-2015-602, ponisio2015farm}, and
promote the persistence and colonization of floral resource
specialists \citep{mgonigle-2015-x}. It is important to understand how
these new species are being incorporated into the network as the
community assembles, and the consequences for interaction patterns and
robustness.

@@

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trials, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. We used
standard techniques to determine whether the assumptions of the models
were met for this and all subsequent models. For the non-assembling
hedgerows and weedy field margins, only sites with five or greater
survey years were included in this analysis (N=11). All statistical
analyses were conducted in R 3.2.3 \citep{R}.

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher is the closeness centrality. We
use linear mixed models to test whether the species closeness
variability (log) is related to the persistence or degree of that
species \citep{lme4, lmetest}. We included random effects for species
and site. Because the degree and persistence of pollinators were
strongly correlated, ($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), we
include each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality, as would
be expected with assembly by preferential attachment, would also lead
to high variability in closeness scores, we also test whether log
closeness centrality increases through time.

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~ S2). We develop a method to examine the temporal
turnover of interactions with weightings based on their similarity. We
followed the algorithm of \cite{ahn2010link} to cluster all the
interactions (edges) hierarchically across sites and years based on
their similarity, and build a dendrogram. The interaction similarity
is based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. We then
use linear models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks
\citep{lme4, lmetest}.

@@

To test whether network modularity, nestedness, connectance or
specialization changed linearly with assembly, we used linear mixed
models with the descriptive network metrics as the response variable,
year of assembly as the explanatory variable, and random effects of
site and year. The number of species in a network affects the patterns
of interaction possible, so we also examined the change in plant and
pollinator species richness through time. We employ generalized linear
mixed models with Poisson error to model richness. We scaled
explanatory variables.

@@

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints},
\ref{fig:changePoints2}).  All five of the assembling hedgerows
experienced network changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows had
significantly more changing points than the non-assembling networks
(estimate of the difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts alone that would effect all networks
similarly.

@@

%Lauren - I changed the first part  of this paragraph but I really don't thinks it is that confusing. The problem is that it is indeed very theoretical, but it is impossible to make our point without being too technical.. I tried to decrease the use of jargons.
Contrary to the general restoration goals, networks' susceptibility 
 to cascading perturbations increased as the communities assembled. We measured vulnerability to cascading perturbations as the algebraic connectivity of the network: the greater the algebraic connectivity, the harder it  is to turn a network into completely disconnected groups of species, and the more vulnerable a community is to cascading perturbations. However, algebraic connectivity is positively related not only to the number of species--- species richness--- but also to the number of interactions in the network--- connectance \citep{gibert2013spatial}. Therefore, the increase in and plant and pollinator richness following
restoration is at least partially responsible for the increase in
response to cascading effects. Additionally, despite the correlation between connectance and algebraic connectivity \citep{gibert2013spatial}, we
observed a decrease in connectance. Thus, topological characteristics of the
networks beyond species richness and connectance are needed to explain
the increased sensitivity to perturbations spreading. These hedgerows
were designed to provide floral resources to the largest number of
pollinators across the growing season \citep{menz-2010-4}. The
generalized nature of the floral community may explain why the
networks tended to be more generalized than expected if interactions
were randomly distributed across species (Fig.~\ref{fig:baci}). In
addition, the design of the hedgerow plantings may have facilitated
the emergence of a single, highly connected module in all of the
networks (see \ref{fig:changePoints2} for examples). This network
configuration results in short path lengths (the distance between
species in a network based on their shared partners), and thus, a
perturbation in one species can more easily spread to other
species. In order to promote more resilient communities, future
restoration efforts should explore designing floral communities to
promote more interaction partitioning using, for example, algorithms
to optimize different network properties based on prior knowledge of
pollinator floral preferences \citep{mgonigle2016tool}, and on desired
network architectures that renders them more robust both to species
loss and to cascading effects.

>>>>

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[the ``rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that phenologically new plant and pollinator species tended to
interact with already well-connected species, potentially because
these species are either more abundant or more temporally
persistent. In addition, using a space-for-time substitution to study
primary succession along a glacier foreland, \cite{albrecht2010plant}
also found some evidence that assembly occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}.  An
increase in nestedness could result from the preferential attachment
process where specialist species attach to the well-connected,
generalist core.

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially ``applied succession''
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. To ensure the continued provision
of ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, kremen-2015-602, ponisio2015farm}, and
promote the persistence and colonization of floral resource
specialists \citep{mgonigle-2015-x}. It is important to understand how
these new species are being incorporated into the network as the
community assembles, and the consequences for interaction patterns and
robustness.

@@

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trials, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type
\citep{lme4}. We used standard techniques to determine whether the
assumptions of the models were met for this and all subsequent
models. For the non-assembling hedgerows and weedy field margins, only
sites with five or greater survey years were included in this analysis
(N=11). All statistical analyses were conducted in R 3.2.3 \citep{R}.

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher the closeness centrality. We use
linear mixed models to test whether the species closeness variability
(log) is related to the persistence or degree of that species
\citep{lme4, lmetest}. We included random effects for species and
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality, as would
be expected with assembly by preferential attachment, would also lead
to high variability in closeness scores, we also test whether log
closeness centrality increases through time.

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species (Fig.~
S2). We develop a method to examine the temporal turnover of
interactions with weightings based on their similarity. We followed
the algorithm of \cite{ahn2010link} to cluster all the interactions
(edges) hierarchically across sites and years based on their
similarity, and build a dendrogram. The interaction similarity is
based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. We then
use linear mixed models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks,
including site as a random effect \citep{lme4, lmetest}.

@@

To test whether network modularity, nestedness, connectance or
specialization changed linearly with assembly, we used linear mixed
models with the descriptive network metrics as the response variable,
year of assembly as the explanatory variable, and random effects of
site and year. The number of species in a network affects the patterns
of interaction possible, so we also examined the change in plant and
pollinator species richness through time. We employ generalized linear
mixed models with Poisson error to model richness \citep{lme4}. We
scaled explanatory variables.

@@

In order to test whether hedgerows changed in robustness as the
communities assembled, the three measures of robustness were modeled
as responses in a linear mixed model with site type as an explanatory
variable and site as a random effect \citep{lme4, lmetest}.

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints},
\ref{fig:changePoints2}).  All five of the assembling hedgerows
experienced network changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows had
significantly more changing points than the non-assembling networks
(estimate of the difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts alone that would have affected all networks
similarly.

@@

% Lauren - I changed the first part of this paragraph but I really
% don't thinks it is that confusing. The problem is that it is indeed
% very theoretical, but it is impossible to make our point without
% being too technical.. I tried to decrease the use of jargons.
Contrary to the general restoration goals, networks' susceptibility to
cascading perturbations increased as the communities assembled. We
measured vulnerability to cascading perturbations as the algebraic
connectivity of the network: the greater the algebraic connectivity,
the more vulnerable a community is to cascading
perturbations. Algebraic connectivity is positively related to both
the number of species and connectance of a network
\citep{gibert2013spatial}. The increase in and plant and pollinator
richness following restoration is thus at least partially responsible
for the increase in response to cascading effects.  Algebraic
connectivity is also positivly correlated with the number in
interactions, or connectance of a network \citep{gibert2013spatial},
We, however, observed a decrease in connectance, suggesting
topological characteristics of the networks beyond just species
richness and connectance are needed to explain the increased
sensitivity to perturbations spreading. These hedgerows were designed
to provide floral resources to the largest number of pollinators
across the growing season \citep{menz-2010-4}. The generalized nature
of the floral community may explain why the networks tended to be more
generalized than expected if interactions were randomly distributed
across species (Fig.~\ref{fig:baci}). In addition, the design of the
hedgerow plantings may have facilitated the emergence of a single,
highly connected module in all of the networks (see
\ref{fig:changePoints2} for examples). This network configuration
results in short path lengths (the distance between species in a
network based on their shared partners), and thus, a perturbation in
one species can more easily spread to other species. In order to
promote more resilient communities, future restoration efforts should
explore designing floral communities to promote more interaction
partitioning using, for example, algorithms to optimize different
network properties based on prior knowledge of pollinator floral
preferences \citep{mgonigle2016tool}, and on desired network
architectures that renders them more robust both to species loss and
to cascading effects.
